Checkpoint 4

### 2020-04-29 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd

\
\

#Sofia's Models:

Variables of Interest: 
\
• per_capita_income
\
•totalTestResults
\
• StateColor
\
• percent_asian
\
•percent_black

##Model 5:

```{r, warning = FALSE, cache=TRUE}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

model_1 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

##Model 6: 
StateColor + per_capita_income + (StateColor | State)
```{r, warning = FALSE, cache=TRUE}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

model_6 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + per_capita_income + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 3, iter = 3000*2
)
```

```{r}
head(data.frame(summary(model_6)),-2)
```

##Model 7: 
StateColor + percent_asian + (StateColor | State)

```{r, warning = FALSE, cache=TRUE}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

model_7 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + percent_asian + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
)
```

```{r}
head(data.frame(summary(model_7)),-2)
```

##Model 8:

StateColor + totalTestResults + (StateColor | State)

```{r, warning = FALSE, cache=TRUE}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

model_8 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + totalTestResults + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
)
```
```{r}
head(data.frame(summary(model_8)),-2)
```

##Model 9:

StateColor +percent_asian + totalTestResults + (StateColor | State)

```{r, warning = FALSE, cache=TRUE}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

model_9 <- stan_glmer(
  ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
)
```

```{r}
head(data.frame(summary(model_9)),-2)
```

>>>>

```{r, warning = FALSE, cache=TRUE}
model_5 <- stan_glmer(
  ChinaVirusInterest ~ Day + totalTestResults + positive + percent_white +  (Day | State),#Random intercepts and slopes when we put Day in
  data = Finaldata, family = gaussian,
  chains = 4, iter = 100, refresh = 0
)
```

```{r}
head(data.frame(summary(model_5),-2))
```
